%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\usepackage{color}
\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'$
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.8]{geometry} % Reduce document margins

%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------
\renewcommand*{\namefont}{\fontsize{25}{1}\mdseries\upshape}
\firstname{Ignacio} % Your first name
\familyname{Alzugaray} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
%\address{B\"ulachstrasse 3, Z\"urich 8057, Switzerland}{Birthdate: 10/11/1992 | Nationality: Spanish}
%\address{Birthdate: 10/11/1992 | Nationality: Spanish}{Z\"urich, Switzerland}
%\address{}{}
%\mobile{+41(0)765124418}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{Email: alzugaray.ign@gmail.com}

\homepage{ialzugaray.github.io/}{Webpage: ialzugaray.github.io} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}
\extrainfo{\\Residence: London, United Kingdom \\ Nationality: Spanish, born 1992}
%\\CV Last Updated: \today}


\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
	\uline{\phantom{#1}}%
	\llap{\contour{white}{#1}}%
}


%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage
%
%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents
%
%\makelettertitle % Print letter title
%
%\lipsum[1-2] % Dummy text
%\lipsum[4] % Dummy text
%
%\makeletterclosing % Print letter signature
%
%\newpage


%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

%Polytechnic University of Catalonia (Barcelona - Spain)	2014-2016
%Excellence scholarship due to academic record. Catalunya-La Pedrera Foundation.
%Major in Robotics. Mean global mark: 8.70/10.
%Thesis: Path planning for MAVs with vision in the loop.
%International student exchange in ETH Zürich (Switzerland)	Feb2016-Aug2016
%Supervised by Prof. Margarita Chli. Mark 5.75 / 6.

\newcommand{\location}[1]{\small{#1}}
\newcommand{\duration}[2]{\footnotesize{#1 - #2}}
\newcommand{\durationsince}[1]{\footnotesize{Since #1}}
\newcommand{\eventdata}[1]{\footnotesize{#1}}

\newcommand{\publication}[6]{
\cventry{[#1]}{}{}{}{}{
	\small{#2.}\\
	\small{\textbf{#3.}}\\
	\small{\textit{#4}, #5}. \small{#6}
}}

\newcommand{\bmvc}{British Machine Vision Conference ({BMVC})}
\newcommand{\threedv}{International Conference on 3D Vision ({3DV})}
%\newcommand{\iros}{Proceedings of the {IEEE/RSJ} Conference on Intelligent Robots and Systems ({IROS})}
\newcommand{\iros}{{IEEE/RSJ} Conference on Intelligent Robots and Systems ({IROS})}
%\newcommand{\icra}{Proceedings of the {IEEE} International Conference on Robotics and Automation ({ICRA})}
\newcommand{\icra}{{IEEE} International Conference on Robotics and Automation ({ICRA})}
\newcommand{\ral}{{IEEE} Robotics and Automation Letters ({RA-L})}
\newcommand{\CVPR}{{IEEE} / CVF Computer Vision and Pattern Recognition Conference ({CVPR})}
\newcommand{\CVPRW}{{IEEE} / CVF Computer Vision and Pattern Recognition Conference ({CVPR}) Workshop}
\newcommand{\ECCV}{European Conference on Computer Vision  ({ECCV})}






%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Research Interest}
\begin{itemize}

	\item \textbf{Efficient Neural SLAM \& Novel Scene Representations:}
	{\small To explore hybrid approaches integrating traditional geometry with AI-driven modules, focusing on real-time performance and enhanced scene understanding.}
	
	
	\item \textbf{Information-guided, Data-Efficient \& Decentralized Spatial AI:} {\small To design distributed systems and agents that reason about space, motion, and action while minimizing communication and computational overhead.} % Sparse
	\item \textbf{Self-supervised and Explainable AI from Large Foundation Models:} {\small To extract and repurpose the knowledge from large pre-trained models for interpretable and generalizable AI solutions.}	
\end{itemize}

\section{Experience}

\newcommand*{\customcventry}[7][.25em]{%
	\cvitem[#1]{#2}{%
		{\bfseries#3}%
%		\vspace{3mm}
%		\hline
%		\vspace{3mm}
		\ifthenelse{\equal{#4}{}}{}{, {\slshape#4}}%
		\ifthenelse{\equal{#5}{}}{}{, #5}%
		\ifthenelse{\equal{#6}{}}{}{, #6}%
		\ifthenelse{\equal{#3#4#5#6}{}}{}{.\strut}%
		\ifx&#7&%
		\else{\ifthenelse{\equal{#3#4#5#6}{}}{}{\newline{}}\begin{minipage}[t]{\linewidth}\small#7\end{minipage}}\fi}}



\cventry{\durationsince{Jul'22}}{Postdoctoral Research Fellow}{\location{Dyson Robotics Lab, Imperial College London}}{}{}{
	\begin{itemize}
		\item Research on parallel and distributed on-pixel processing for visual SLAM.
		\item Research on 3D implicit representations for self-supervised scene understanding.
		\item Supervisor: Prof. Dr. Andrew Davison.
	\end{itemize}
}

\cventry{\duration{Mar'22}{Jun'22}}{Postdoctoral Researcher}{\location{Vision for Robotics Lab (V4RL), ETH Z\"urich}}{}{}{
	\begin{itemize}
		\item Research on asynchronous, event-driven algorithms for visual SLAM using event cameras.
		\item Designing of decentralized multi-agent visual SLAM architecture using distributed processing.
		\item Supervisor: Prof. Dr. Margarita Chli.
	\end{itemize}
}


\cventry{\duration{Sep'21}{Jun'22}}{Research Scientist}{\location{Facebook/Meta Reality Labs}}{}{}{
	\begin{itemize}
		\item Designing of a NeRF-based pipeline for image-based visual relocalization.
		\item PyTorch implementation trained with real egocentric footage for AR applications.
		\item Intern position during Sept'21-Dec'21. External contractor position during Mar'22-Jun'22.				
		\item Supervisors: Dr. Vasileios Balntas and Dr. Armen Avetisyan.
	\end{itemize}
}{}

\cventry{\duration{Sep'19}{Jun'19}}{Software Engineer Intern}{\location{Disney Research Zurich}}{}{}{
	\begin{itemize}
		\item Development of VR animation tools with hand tracking and gesture recognition within Unity.
		\item Close collaboration with Disney Animation Studio on \httplink[\color{blue}PoseVR project]{www.disneyanimation.com/technology/posevr/}.
		\item Supervisors: Dr. Jakob Buhmann and Dr. Martin Guay.
	\end{itemize}
	}{}


\cventry{\duration{Sep'16}{Feb'17}}{Research Assistant}{\location{Vision for Robotics Lab (V4RL), ETH Z\"urich}}{}{}{
	\begin{itemize}
		\item Implementation of probabilistic event-based scene mapping.
		\item Design of active monocular-inertial SLAM pipeline for UAVs.
		\item Supervisor: Prof. Dr. Margarita Chli.
	\end{itemize}
}

\cventry{\duration{Jun'15}{Feb'16}}{Research Assistant Intern}{\location{Institute of Robotics and Industrial Informatics (IRI-CSIC)}}{}{}{
	\begin{itemize}
		\item Design of path planning algorithms for UAVs embedding the experience of expert pilots.
		%\item Accepted paper in the International Conference on Intelligent Robots and Systems (IROS 2016).
		\item Supervisor: Prof. Dr. Alberto Sanfeliu.
	\end{itemize}
}{
}


%\cventry{\duration{Oct'13}{Jul'14}}{Undergraduate Research Assistant}{\location{ 		Instituto Andaluz de Autom\'atica Avanzada y Rob\'otica}}{}{}{
%	\begin{itemize}
%	\item Design of trajectory control algorithms for robotic manipulators applied to laparoscopic surgery.
%	\item Supervisor: Dr. Carlos Perez del Pulgar.
%\end{itemize}
%}{
%}


%\subsection{Teaching Experience}

%\cventry{Present 09/2016}{Master's Thesis Student Supervisor}{}{}{}{\textit{ETH Z\"urich -- Vision for Robotics Lab (V4RL), Switzerland}\\- \textit{Path planning for UAVs with Visual-Inertial SLAM}. Collaboration with IBM Z\"urich.\\- \textit{Improved Visual SLAM with event-based cameras}.}{}



%\cventry{07/2015 01/2015}{Teaching Assistant Intern}{}{}{}{\textit{Polytechnic University of Catalonia (UPC), Spain}\\Department of Mechanical Engineering and Department of Thermal Engines and Machines. Creation, updating and maintenance of digital content for new courses.}{}

%\cventry{Sep 2013\\Jul 2013}{Undergraduate Teaching Assistant Intern}{}{}{}{\textit{Department of Applied Mathematics. University of Malaga (UMA), Spain}\\Simulation of numerical methods applied to differential equations for teaching purposes.\\Supervisor: Prof. Jose Manuel Gonzalez Vida.}{}

%\cventry{07/2012 02/2012}{Undergraduate Electronic Lab Assistant}{}{}{}{\textit{Department of Electronics. University of Malaga (UMA), Spain}\\ Teaching support during students' practices and maintenance of electronic equipment.}{}

%\subsection{Vocational}

%\cventry{07/2013}{Participant in the \textit{International Summer School in Microtechnology}}{}{}{}{\textit{Albert-Ludwigs Universit\"at Freiburg, Germany}}

%\cventry{07/2013 12/2012}{Contestant in Spanish Control Committee (CEA-IFAC) XXXIV Competition}{}{}{}{\textit{Department of Systems Engineering and Automatics. University of Malaga (UMA), Spain}\\ Modelling of multirotor UAVs and designing  of way-point path planning algorithms. \\Supervisor: Anthony Mandow.}{}

%\cventry{05/2012 09/2011}{Member of Student's Group UMA TROTA Electric}{}{}{}{\textit{Department of of Electronics. University of Malaga (UMA)}\\ Evaluation of control strategies applied to electric powered vehicles for competition.}{}


\section{Education}


\cventry{\small{2022}}{Ph.D. in Computer Vision}{\location{Vision for Robotics Lab (V4RL), ETH Z\"urich}}{}{}{ 
	%Asynchronous Event-based SLAM for Real-Time Robotic Applications.
	Thesis: \textit{Event-driven Feature Detection and Tracking for Visual SLAM}.
	\begin{itemize}
		\item 	Advisor: Prof. Dr. Margarita Chli.
		\item Examiners: Prof. Dr. Andrew Davison, Prof. Dr. Davide Scaramuzza, Prof. Dr. Laurent Kneip.
	\end{itemize}
}

\cventry{\small{2016}}{M.Sc. Automatic Control and Robotics}{\location{Polytechnic University of Catalonia (UPC)}}{}{}{
	Top student in Master's program (2014-2016), GPA -- 8.70/10.\\
	Thesis: \textit{Path planning for MAVs with vision in the loop.}
	\begin{itemize}
		\item 	Advisor: Prof. Dr. Margarita Chli. Grade: 5.75/6. ETH Z\"urich -- International student exchange.
		%\item 	Accepted as a paper in the \textit{International Conference on Robotics and Automation}  (ICRA 2017).
	\end{itemize}
}

\cventry{\small{2014}}{B.Sc. Industrial Engineering}{\location{University of Malaga (UMA)}}{}{}{Top student in Bachelor's program (2010-2014). GPA -- 8.49/10.\\
	Thesis: \textit{Teleoperation of Robotic Manipulators applied to Laparoscopic Surgery.}
	\begin{itemize}
		\item Advisor: Dr. Carlos Perez del Pulgar. Grade: 9.5/10. 
	\end{itemize}
}




\section{Research and Dissemination Activities}


\subsection{Chairing}
\cvitem{\eventdata{Oct'24}}{\textbf{Session Chair} for \textit{Multi-Robot Systems III}, Oral Session,  IROS'24}

\cvitem{\eventdata{May'24}}{\textbf{Session Chair} for \textit{Perception for Grasping and Manipulation III}, Oral Session,  ICRA'24}


\subsection{Invited Talks \& Workshops}
\cvitem{\eventdata{Oct'21}}{\textbf{Invited Talk} at the \httplink[Robotic and Perception Group]{rpg.ifi.uzh.ch/}, ETH Zurich / University of Zurich. Presentation title: ``Event-Driven Feature Detection and Tracking for Robotic Applications.''}

\cvitem{\eventdata{Jun'21}}{\textbf{Invited Speaker} at the \textit{Event-based Vision} workshop, CVPR 2021. Presentation title: ``Towards Asynchronous SLAM with Event Cameras.''}
\cvitem{\eventdata{Oct'18}}{\textbf{Invited Speaker} at the \textit{Unconventional Sensing and Processing for Robotic Visual Perception} workshop, IROS 2018. Presentation title: ``Asynchronous Vision.''}

\subsection{Others}
\cventry{\eventdata{May'25}}{External PhD. Thesis Examiner}{}{\location{Institute of Robotics and Industrial Informatics (IRI-CSIC)}}{}{Thesis: ``Bio-inspired Event-driven Intelligence for Motion Estimation'' by Yi Tian.}{}
\cventry{\durationsince{2016}}{Supervision of Students and Researchers}{\location{ETH Z\"urich / Imperial College London}}{}{}{
	\begin{itemize}
	\item Supervised over 35 graduate student projects.
%\item Currently supervising other researchers on continuous-time SLAM and decentralized visual SLAM.
\item Shared supervision of doctoral students on SLAM, scene understanding and 3D geometry.
	\end{itemize}
}

\cventry{\durationsince{2016}}{Reviewer of Scientific Publications}{}{}{}{ICRA, IROS, 3DV, BMVC, ECCV, ICCV, CVPR, MVA, RSS, T-RO, T-PAMI, RA-L, IJCV.}{}


%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
\section{Awards and Scholarships}


\cventry{\small{2016}}{{Award for Academic Performance in Master's}}{\location{Polytechnic University of Catalonia (UPC)}}{}{}{
Granted to the top performing student in postgraduate programme (2014--2016). The recipient is granted with an internship sponsored by KUKA AG.}{
}

\cventry{\small{2016}}{International Student Scholarship}{\location{ETH Z\"urich, Swiss-European Mobility Programme}}{}{}{Competitive scholarship granted to students in an international exchange programme.}{
}

\cventry{\small{2014}}{Excellence Scholarship in Master's Programme}{\location{ Catalunya-La Pedrera Foundation}}{}{}{ Two-years scholarship granted to the Master's program applicant with the best academic record.}{
}


\cventry{\small{2014}}{Award for Academic Performance in Bacherlor's}{\location{University of Malaga (UMA)}}{}{}{ Granted to the top performing student in undergraduate programme (2010--2014).}{
}

\cventry{\small{2013}}{Undergraduate Research Scholarship}{\location{University of Malaga, Spanish Ministry of Education}}{}{}{	 Nationally competitive scholarship to conduct six-months research projects.}{}


%\section{Skills}
%\cvitem{Languages}{\textbf{Spanish:} Native \hfill \textbf{English:} Professional Proficiency \hfill \textbf{German:} Basic}
\newpage
\section{Languages}
\cvitemwithcomment{Spanish}{Native}{}
\cvitemwithcomment{English}{Professional Proficiency}{B2.2 University of Cambridge (2013)}
\cvitemwithcomment{German}{Intermediate}{B1.1 University of Z\"urich (2017)}


\vfill
\section{Skills}
\cvitem{Programming}{Python, C++, CUDA, \textsc{Matlab}, C\#, \textsc{Simulink}, \LaTeX}
\cvitem{Frameworks} {PyTorch, OpenCV, ROS, Unity, Unreal Engine, Gazebo, Blender, Git}
\cvitem{Technologies}{NeRFs, Gaussian Splatting, Diffusion Models, Gaussian Belief Propagation, ADMM}
%\cvitem{Industrial}{NI LabView, Beckhoff TwinCAT, ARENA, St\"aubli VAL3, SolidEdge}


\vfill
\section{Software Releases}
%\cventry{2018}{{}{C++}}{}{}{

\cventry{\small{2021}}{HASTE: Event-driven Feature Tracking and Optimization}{}{in C++}{}{\url{github.com/ialzugaray/haste}}{
}
\cventry{\small{2019}}{Arc*: Event-driven Corner-Event detector}{}{in C++/ROS}{}{\url{github.com/ialzugaray/arc_star_ros}}{
}

\section{Publications}

%\publication{C8}{	\myuline{I. Alzugaray}$^{*}$, A. Schneebeli$^{*}$, R. Mascaro, A. Sabater, A.C. Murillo and M. Chli}{Graph Neural Networks for Corner Detection with Event Cameras}{\icra}{2022}{\textit{Under Review.}}



\subsection{Conferences \& Workshops}

\publication{\httplink[\color{blue}C13]{arxiv.org/abs/2406.09726}}{
	\myuline{I. Alzugaray}, R. Murai, A. Davison}{PixRO: Pixel-Distributed Rotational Odometry with Gaussian Belief Propagation}{\CVPR, International Workshop on Computational Cameras and Displays (CCD)}{Seattle, 2024}{}

\publication{\httplink[\color{blue}C12]{www.ecva.net/papers/eccv_2024/papers_ECCV/papers/04347.pdf}}{
D. Hug, \myuline{I. Alzugaray}, M. Chli}{Hyperion – A fast, versatile symbolic Gaussian Belief Propagation framework for Continuous-Time SLAM}{\ECCV}{Milan, 2024}{}

\publication{\httplink[\color{blue}C11]{www.robot-learning.uk/dream2real}}{
	I. Kapelyukh, Y. Ren, \myuline{I. Alzugaray}, E. Johns}{Dream2Real: Zero-Shot 3D Object Rearrangement
	with Vision-Language Models}{\icra}{Yokohama, 2024}{}

\publication{\httplink[\color{blue}C10]{marwan99.github.io/Fit-NGP/}}{
	 M. Taher  \myuline{I. Alzugaray}, A. Davison}{Fit-NGP: Fitting Object Models to Neural Graphics Primitives}{\icra}{Yokohama, 2024}{}


\publication{\httplink[\color{blue}C9]{ieeexplore.ieee.org/document/10160941}}{
P. B{\"a}nninger,  \myuline{I. Alzugaray}, M. Karrer, M. Chli}{Cross-Agent Relocalization for Decentralized Collaborative SLAM}{\icra}{London, 2023}{}


\publication{\httplink[\color{blue}C8]{arxiv.org/abs/2303.02672}}{C. Le Gentil, \myuline{I. Alzugaray}, T. Vidal-Calleja}{Continuous-Time Gaussian Process Motion-Compensation for Event-Vision Pattern Tracking with Distance Fields}{\icra}{London, 2023}{}


\publication{\httplink[\color{blue}C7]{www.bmvc2020-conference.com/conference/papers/paper_0744.html}}{\myuline{I. Alzugaray} and M. Chli}{{HASTE}: multi-Hypothesis Asynchronous Speeded-up Tracking of Events}{\bmvc}{Virtual, 2020}{}



\publication{\httplink[\color{blue}C6]{doi.org/10.1109/IROS45743.2020.9341208}}{
	C. Le Gentil, F. Tschopp, \myuline{I. Alzugaray}, T. Vidal-Calleja, R. Siegwart and J. Nieto}{
	IDOL: A framework for IMU-DVS odometry using lines}{\iros}{Las Vegas, NV, USA, 2020}{}


\publication{\httplink[\color{blue}C5]{doi.org/10.3929/ethz-b-000360434}}{\myuline{I. Alzugaray} and M. Chli}{Asynchronous Multi-hypothesis Tracking of features with Event Cameras}{\threedv}{Quebec, Canada, 2019}{Oral presentation.}


\publication{\httplink[\color{blue}C4]{doi.org/10.3929/ethz-b-000291763}}{\myuline{I. Alzugaray} and M. Chli}{{ACE}: An Efficient Asynchronous Corner Tracker for Event Cameras}{\threedv}{Verona, Italy, 2018}{}



\publication{\httplink[\color{blue}C3]{doi.org/10.1007/978-3-319-67361-5_13}}{L. Texeira, \myuline{I. Alzugaray} and M. Chli}{Autonomous Aerial Inspection Using Visual-Inertial Robust Localization and Mapping}{Conference on Field and Service Robotics ({FSR})}{Zurich, Switzerland, 2017}{}


\publication{\httplink[\color{blue}C2]{doi.org/10.3929/ethz-a-010862339}}{\myuline{I. Alzugaray}, L. Texeira and M. Chli}{Short-term UAV Path-Planning with Monocular-Inertial SLAM in the Loop}{\icra}{Singapore, 2017}{}


\publication{\httplink[\color{blue}C1]{www.iri.upc.edu/files/scidoc/1779-Learning-the-Hidden-Human-Knowledge-of-UAV-Pilots-when-navigating-in-a-cluttered-environment-for-improving-Path-Planning.pdf}}{\myuline{I. Alzugaray} and A. Sanfeliu}{Learning the Hidden Human Knowledge of UAV Pilots when navigating in a cluttered environment for improving Path Planning}{\iros}{Daejeon, Korea, 2016}{}




\subsection{Journals}

\publication{\httplink[\color{blue}J5]{doi.org/10.1007/s10846-025-02223-6}}{
	L. Yang, R. Mascaro, \myuline{I. Alzugaray}, S.M. Prakhya, M. Karrer, Z. Liu, M. Chli}
{LiDAR Loop Closure Detection using Semantic Graphs with Graph
	Attention Networks}
{Journal of Intelligent \& Robotic Systems}{2025}{}


\publication{\httplink[\color{blue}J4]{arxiv.org/abs/2401.15036}}{
	R. Murai, \myuline{I. Alzugaray}, P.H.J. Kelly, A. Davison}{Distributed Simultaneous Localisation and Auto-Calibration using Gaussian Belief Propagation}{\ral}{ 2024}{}

\publication{\httplink[\color{blue}J3]{doi.org/10.3929/ethz-b-000549482}}{D. Hug, P. B{\"a}nninger, \myuline{I. Alzugaray} and M. Chli}{Continuous-Time Stereo-Inertial Odometry}{\ral}{2022}{}

\publication{\httplink[\color{blue}J2]{doi.org/10.1016/j.ymssp.2020.106905}}{Z. Lai, \myuline{I. Alzugaray}, M. Chli and E. Chatzi}{Full-field structural monitoring using event cameras and physics-informed sparse identification}{Mechanical Systems and Signal Processing}{2020}{}

\publication{\httplink[\color{blue}J1]{doi.org/10.3929/ethz-b-000277131}}{\myuline{I. Alzugaray} and M. Chli}{Asynchronous Corner Detection and Tracking for Event Cameras in Real Time}{\ral}{2018}{}

\subsection{Doctoral Thesis}
\publication{\httplink[\color{blue}T]{www.research-collection.ethz.ch/handle/20.500.11850/541700}}{\myuline{I. Alzugaray}}{Event-driven Feature Detection and Tracking for Visual SLAM}{ETH Zurich}{2022}{}



%\section{Interests}
%\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
%\cvlistdoubleitem{Cooking}{Reading}
%\cvlistdoubleitem{Jazz}{Hiking}





%\section{Delete}
%
%\cventry{2012--Present}{1\textsuperscript{st} Year Analyst}{\textsc{Lehman Brothers}}{Los Angeles}{}{Developed spreadsheets for risk analysis on exotic derivatives on a wide array of commodities (ags, oils, precious and base metals), managed blotter and secondary trades on structured notes, liaised with Middle Office, Sales and Structuring for bookkeeping.
%\newline{}\newline{}
%Detailed achievements:
%\begin{itemize}
%\item Learned how to make amazing coffee
%\item Finally determined the reason for \textsc{PC LOAD LETTER}:
%\begin{itemize}
%\item Paper jam
%\item Software issues:
%\begin{itemize}
%\item Word not sending the correct data to printer
%\item Windows trying to print in letter format
%\end{itemize}
%\item Coffee spilled inside printer
%\end{itemize}
%\item Broke the office record for number of kitten pictures in cubicle
%\end{itemize}}
%
%%------------------------------------------------
%
%\cventry{2011--2012}{Summer Intern}{\textsc{Lehman Brothers}}{Los Angeles}{}{Rated "truly distinctive" for Analytical Skills and Teamwork.}
%
%%------------------------------------------------
%
%\subsection{Miscellaneous}
%
%\cventry{2010--2011}{}{}{}{}{Spent some time finding myself. This was a courageous endeavour that didn't have a job title. It was quite important to my overall development though so I'm adding it to my CV. Also it explains the gap in my otherwise stellar CV.}
%
%\cventry{2009--2010}{Computer Repair Specialist}{Buy More}{Burbank}{}{Worked in the Nerd Herd and helped to solve computer problems. Allowed me to become expert in all forms of martial arts and weaponry.}
%
%
%%----------------------------------------------------------------------------------------
%%	COMPUTER SKILLS SECTION
%%----------------------------------------------------------------------------------------
%
%\section{Computer skills}
%
%\cvitem{Basic}{\textsc{java}, Adobe Illustrator}
%\cvitem{Intermediate}{\textsc{python}, \textsc{html}, \LaTeX, OpenOffice, Linux, Microsoft Windows}
%\cvitem{Advanced}{Computer Hardware and Support}
%
%%----------------------------------------------------------------------------------------
%%	COMMUNICATION SKILLS SECTION
%%----------------------------------------------------------------------------------------
%
%\section{Communication Skills}
%
%\cvitem{2010}{Oral Presentation at the California Business Conference}
%\cvitem{2009}{Poster at the Annual Business Conference in Oregon}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------







\end{document}
